Cartogram Mapping and its Application to Cancer Data Visualisation

### 2019-08-20 review_article.Rmd
delete chloropleth folder

choropleth_grid <- gridExtra::grid.arrange(
  grid::rasterGrob(plot1), 
  grid::rasterGrob(plot2), 
  grid::rasterGrob(plot3), 
  grid::rasterGrob(plot4), 
  grid::rasterGrob(plot5), 
  grid::rasterGrob(plot6),
  grid::rasterGrob(plot7), 
  grid::rasterGrob(plot8), 
  grid::rasterGrob(plot9),
  grid::rasterGrob(plot10),
  grid::rasterGrob(plot11), 
  grid::rasterGrob(plot12),
  grid::rasterGrob(plot13), 
  grid::rasterGrob(plot14), 
  grid::rasterGrob(plot15),
  grid::rasterGrob(plot16),
  grid::rasterGrob(plot17))

>>>>

choropleth_grid <- gridExtra::grid.arrange(
  grid::rasterGrob(plot1), 
  grid::rasterGrob(plot2), 
  grid::rasterGrob(plot3), 
  grid::rasterGrob(plot4), 
  grid::rasterGrob(plot5), 
  grid::rasterGrob(plot6),
  grid::rasterGrob(plot7), 
  grid::rasterGrob(plot8), 
  grid::rasterGrob(plot9),
  grid::rasterGrob(plot10),
  grid::rasterGrob(plot11), 
  grid::rasterGrob(plot12),
  #grid::rasterGrob(plot13), 
  grid::rasterGrob(plot14), 
  grid::rasterGrob(plot15),
  grid::rasterGrob(plot16),
  grid::rasterGrob(plot17))
